\documentclass{../resources/cranfieldChart}

\begin{document}

\maketitleSimple

\section*{Details}
{\centering
\begin{tabular}{|c|c|c|}
    \hline
     Date & Attending & Report writer \\\hline
     \begin{tabular}{c}
     	11/01/2015\\
     	11:30am - 12:10pm
     \end{tabular} & 
     \begin{tabular}{c}
     	Diaferia Quentin\\
     	Levasseur Thibaud\\ 
     	Pei Wang\\
     	Perez Bada Gonzalo
     \end{tabular} & 
     Thibaud Levasseur \\\hline
\end{tabular}
\par}
\section*{Agenda}
The following topics were discuss in this meeting :
\begin{itemize}
	\item Question to the IT department;
	\item Client definition;
	\item Work split.
\end{itemize}


\section*{Question to the IT department}
After the last meeting, the whole group went to the IT department to ask if there were any kind of agreement between private companies and Cranfield related to the use of the Grid or Astral.
\paragraph{} As a lot of licence are bought as educational, it is not legal to resell it to private entities. Thus the software we aim to create will not be sold as a SaaS to the end user.

\section*{Client definition}
As the IT department said, our software could not be set on a SaaS business model unless we buy our own computational infrastructure. 
\paragraph{}Thibaud raised the idea to actually sell the software to the owner of the computational resources and not to the end user. So, each entity willing to give to its user an easy interface to use instead of a command line terminal might be interested by our application.


\section*{Work split}
Short term objectives were define during this meeting, with piece of work splitting among the team.

\paragraph{Diaferia Quentin}
\begin{itemize}
	\item Organizes Git repository;
	\item Writes  the requirements of the upload and download of files;
	\item Commits his work on Github;
	\item Implement the Login on Astral
\end{itemize}

\paragraph{Levasseur Thibaud}
\begin{itemize}
	\item Writes  the requirements of the authentication;
	\item Commits his work on Github;
	\item Implement the Login on Astral
\end{itemize}

\paragraph{Pei Wang}
\begin{itemize}
	\item Register on Github and learn how to use it;
	\item Register on Trello and learn how to use it;
	\item Writes  the display requirements;
	\item Writes  the non functional requirements;

\end{itemize}

\paragraph{Perez Bada Gonzalo}
\begin{itemize}
	\item Writes  the requirements of the script use (Metis);
\end{itemize}

\paragraph{} The team aims to go through all those task before our next meeting at the beginning of the next week.

\end{document}