\documentclass{../resources/cranfieldChart}

\begin{document}

\maketitleSimple

\section*{Details}
{\centering
\begin{tabular}{|c|c|c|}
    \hline
     Date & Attending & Report writer \\\hline
     \begin{tabular}{c}
     	11/01/2015\\
     	3:30pm - 4:00pm
     \end{tabular} & 
     \begin{tabular}{c}
     	Diaferia Quentin\\
     	Levasseur Thibaud\\ 
     	Pei Wang\\
     	Perez Bada Gonzalo
     \end{tabular} & 
     Diaferia Quentin \\\hline
\end{tabular}
\par}
\section*{Agenda}

\begin{itemize}
	\item Debriefing about the first week
	\item Tools
	\item Legal aspects
	\item Priorities
\end{itemize}

\section*{Debriefing about the first week}

\paragraph{}
Our goal is to realise a web application which is an graphic interface for Astral. It means that our users need to have an Astral account.

\paragraph{}
A prototype of the interface has been made using a bootstrap template and is available on Quentin's public web space : http://public.cranfield.ac.uk/s242734/meshslicer/pages/index.html

\paragraph{}
Thibaud has began to work on an algorithm to display a graph. It works, but it is extremely slow as the graph contains millions of vertices. It might be useless to display the whole graph, using a coarsened one should be enough to have a preview of the partitioned graph.

\section*{Tools}

\paragraph{}
We have set up a Trello and a Github repository to help us with the project management and the development. Fanny does not have her accounts yet, but will create them and learn to use those tools.

\paragraph{}
A technical issue about how to use SSH on a web application has been raised, but after a short research, we found that some PHP libraries exist and are easy to use.

\section*{Legal aspects}

\paragraph{}
Is it possible to "sell" an Astral account in addition of our web app to our customer ? We have to study the legal aspect. We are considering three different kinds of customers :
\begin{itemize}
	\item People having an Astral account
	\item People having their own HPC facility
	\item People not having any Astral account
\end{itemize}

\section*{Priorities}

\paragraph{}
We will visit the Cranfield IT department to ask whether it is possible to have an agreement with an external company to use Astral.

\paragraph{}
As soon as this question is answered, we will meet again to discuss the requirements and split the work.

\end{document}