\documentclass{../resources/cranfieldChart}

\begin{document}

\maketitleSimple

\section*{Details}
{\centering
\begin{tabular}{|c|c|c|}
    \hline
     Date & Attending & Report writer \\\hline
     \begin{tabular}{c}
     	04/03/2015\\
     	10:30am - 10:45pm
     \end{tabular} & 
     \begin{tabular}{c}
     	Diaferia Quentin\\
     	Levasseur Thibaud\\ 
     	Pei Wang\\
     	Perez Bada Gonzalo
     \end{tabular} & 
     Thibaud Levasseur \\\hline
\end{tabular}
\par}
\section*{Agenda}
The following topics were discuss in this meeting :
\begin{itemize}
	\item What have been done;
	\item What is left to do.
	
\end{itemize}


\section*{What have been done}
\paragraph{Interface}
The interface is almost done : downloading a file has still some issues. The file stay on the server after copied from Astral. It is required to be deleted at some point.
\paragraph{Configuration file}
Creating the configuration file is now possible through the application.
\paragraph{C program}
The program is working on both mesh and graphs. It is now properly documented
\paragraph{Graph displayer}
The display works independently from the Interface. It reduces the size of the graph and color it properly. It needs to be integrated in the interface. Mesh file are not yet taken into account.

\section{What is left to do}
The following point are still to be done :
\begin{itemize}
	\item Integrate the graph displayer;
	\item Create the link between the interface and the program;
	\item Fill up the landing page advertising;
	\item Adapt the graph displayer to meshes;
	\item Parse the output file;
	\item Test the program in order to find possible bugs.
\end{itemize}

\end{document}